\documentclass[11pt]{article}
\usepackage[letterpaper,
top=0.4in,
bottom=0.4in,
left=0.5in,
right=0.5in]{geometry}
                       
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{titlesec}
\raggedright
\pagestyle{empty}

\input{glyphtounicode}
\pdfgentounicode=1

\titleformat{\section}{\bfseries\large}{}{0pt}{}[\vspace{1pt}\titlerule\vspace{-6.5pt}]

\renewcommand\labelitemi{$\vcenter{\hbox{\small$\bullet$}}$}
\setlist[itemize]{itemsep=-2pt, leftmargin=12pt, topsep=5pt}

\begin{document}

% name
\begin{center}
\LARGE \textbf{Karthik Vinayan}
\end{center}

\vspace{3pt}

% contact information
\centerline{\href{mailto:karthikvinayan57@gmail.com}{karthikvinayan57@gmail.com} \hspace{0.5em} | \hspace{0.5em} Hyderabad, IN \hspace{0.5em} | \hspace{0.5em} \href{https://linkedin.com/in/karthik-vinayan}{LinkedIn} \hspace{0.5em} | \hspace{0.5em} \href{https://github.com/o1x3}{GitHub} \hspace{0.5em} | \hspace{0.5em} \href{https://o1x3.com}{o1x3.com}}

\vspace{-10pt}

% summary
\section*{Summary}
Founding engineer who built the AI backend for a cloud automation platform from ground zero — now weeks from launch. Own a 20-agent orchestration system, real-time sync architecture, and full ML infrastructure. Lead code reviews, mentor engineers, and sync daily with founders. Thrive on bleeding-edge problems and fast iteration.

\vspace{-6.5pt}
\section*{Experience}

\textbf{Founding Software Engineer — AI \& Backend Systems} \hfill Jan 2025 -- Present \\
{\small Omni RPA Inc / Agentic Solutions Pvt Ltd — San Jose / Hyderabad}
\begin{itemize}
  \item Built core AI backend from scratch for a platform replacing cloud architects — users configure AWS/Azure/GCP infrastructure via chat while context graph and cost calculator update live; one-click deployment. Onboarded first enterprise client (Arrcus Cloud); launching publicly in weeks.
  \item Architected 20+ agent system: main orchestration agent coordinates tool calling, function execution, and RAG retrieval while ambient agents maintain shared context graph consistency across all user interactions in real-time.
  \item Built "hive mind" sync layer — websockets and event-driven architecture keep chat, context graph, live cost calculator, and UI synchronized; sub-second latency throughout.
  \item Designed hybrid graph architecture (Neo4j + FalkorDB) powering millions of nodes with sub-2s query latency; built orchestration layer over cloud SKU pricing APIs serving millions of data points to agents.
  \item Built async document ingestion pipeline (Python, NATS JetStream) processing hundreds of thousands of PDF pages into searchable knowledge graph for RAG; manage Supabase for session storage; built custom eval framework.
  \item Own 3-5 repositories end-to-end: manage all PRs/issues, containerize and ship to production, on-call for incidents. Debugged through countless production issues to reach stable operation.
  \item Lead cross-functional work across every team (frontend, data, Java backend, DevOps); mentored 2 interns, onboarded engineers, write technical specs. Demo to clients; sync daily with founders.
\end{itemize}

\vspace{-18.5pt}

\section*{Open Source \& Projects}
\textbf{\href{https://github.com/o1x3/ctoken}{ctoken}} — OpenAI API cost estimation library published on PyPI. Supports all models, streaming, caching breakdown. MIT licensed, CI/CD, full test suite. \\[4pt]
\textbf{iOS Apps (In Development)} — Building two apps with on-device AI using Apple Foundation Models: health/fitness tracker and personal finance manager. Shipping Q1 2026. \\[4pt]
\textbf{Crop Ripeness Detection (Research Intern)} — Built real-time detection system using YOLOv8 fine-tuned on proprietary agricultural dataset; deployed to production at Digital University of Kerala.

\vspace{-6.5pt}

\section*{Publication}
\textbf{Automated Medicine Delivery System for Hospitals} — Springer LNNS, 2025 \\
{\small Led team building Raspberry Pi autonomous robot with obstacle detection, path following, and RFID room ID. \href{https://doi.org/10.1007/978-981-96-3652-5\_40}{DOI: 10.1007/978-981-96-3652-5\_40}}

\vspace{-6.5pt}

\section*{Skills \& Certifications}
\textbf{Certifications:} AWS Certified Cloud Practitioner, Microsoft Azure Administrator (AZ-104) \\
\textbf{Languages:} Python, SQL, C, C++, Java, Swift (learning) \\
\textbf{AI/ML:} Multi-Agent Systems, LLM Orchestration, Tool/Function Calling, RAG, Eval Frameworks, MCP, PyTorch \\
\textbf{Backend:} Async Python, Websockets, Event-Driven, FastAPI, NATS, Neo4j, FalkorDB, Supabase, Redis \\
\textbf{Cloud \& DevOps:} AWS, Azure, GCP, Docker, Kubernetes, CI/CD

\vspace{-6.5pt}
\section*{Education}
\textbf{Vellore Institute of Technology} -- B.Tech CSE, AI \& ML Specialization \hfill Sep 2021 -- Aug 2025

\end{document}
